### 2015-02-05 fundamentals/examples.tex
minor edits

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
modified open and closed cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the modified open case and every 9
cycles (180 months) for the closed case.  Because the modified open scenario
does not re-recycle material, it takes the fabrication facility 1 cycle longer
to accumulate a full batch of fissile material.

>>>>

Figure \ref{fig:puseries1} shows the full-system plutonium buildup for open
(no recycle), modified open, and closed (infinite-pass recycle) variations of
the one-reactor scenario described above. The figure was generated directly
from \Cyclus output data. After several batch cycles (near month 300) in the
modified open and closed cases, enough separated fissile material accumulates
in the fuel fabrication facility to generate a full recycled batch.  When this
batch is transmuted, more plutonium is burned than created.  This results in a
drop in the total fuel cycle system plutonium inventory.  This pattern repeats
roughly every 10 cycles (200 months) for the modified open case and every 9
cycles (180 months) for the closed case.  Because the modified open scenario
does not re-recycle material, it takes the fabrication facility 2 cycles longer
to accumulate a full batch of fissile material.
